Modeling vertical-axis cross-flow turbine wakes

### 2015-08-13 paper.tex
Add perf figure

>>>>

In this study we seek to predict the near-wake of the UNH-RVAT turbine,
experimental performance curves for which are shown in
Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient.

    \includegraphics[width=0.9\textwidth]{figures/exp_perf}

    \caption{Mean rotor power (left) and drag (right) coefficient curves from
        the tow tank experiments\cite{Bachant2015-RVAT-Re-dep-data}.}

    \label{fig:exp_perf}
\end{figure}
